\documentclass[12pt]{article}
\begin{document}

\begin{document}

\section{Silicate melting}
\subsubsection*{Walker and Agee (1988) \cite{Walker1988}:}
\begin{enumerate}
    \item Conditions: 1.5 GPa and 1370-1410C
    \item Note the difference in wetting properties between silicate and sulfide melts
    \item Talk about thermal migration
    \item Use Allende composition
\end{enumerate}

\subsubsection*{Jurewicz et al. (1993) \cite{Jurewicz1993}:}
\begin{enumerate}
    \item Melting experiments on Allende
    \item Good place to start on silicate solidus
    \item Tracks the phase abundances as function of T
\end{enumerate}



\subsubsection*{McSween (1989) \cite{McSween1989}:}
\begin{enumerate}
    \item good sumary of silicate phase relations.
    \item Eucrites are close to the eutectic melt of \cite{Stolper1977}
\end{enumerate}



\section{Silicate-metal melt mobility}

\subsubsection*{Holzheid (2000) \cite{Holzheid2000}:}
\begin{enumerate}
    \item Conditions: 1.5 GPa and 1370-1410C
    \item sulfide melt adheres to olivine grain boundaries
    \item sulfide diffusion through silicate melt/greedy giant
    \item metal-silicate wetting angle is controlled by light element content
\end{enumerate}

\subsubsection*{Bagdassarov et al. (2009) \cite{Bagdassarov2009b}}
\begin{enumerate}
    \item Metal-silicate differentiation experiments
    \item Silicate melt allow migration of metalic melt
    \item increase of migration velocity above 15\% metallic melt.
\end{enumerate}

\subsubsection*{Holzheid (2013) \cite{Holzheid2013}}
\begin{enumerate}
    \item wetting angles in metal-silicate-olivine sytems
    \item FeS is not fully non-wetting
    \item Concludes FeS does not connect in partialy molten silicate
\end{enumerate}


\subsection{Dynamic models of planetesimal differentiation}
\subsection{Preliminary results on the dynamics of planetesimal differentiation}
\section{Proposed study}
\subsection{Outstanding science questions}
Important planetary science questions:
\begin{enumerate}
    \item What is the effect of silicate melting on the thermal structure of planetesimals?
    \item Does silicate melting promote or hinder metal-silicate differentiation?
    \item 
\end{enumerate}
To answer these planetary science questions requires that we address the following fundamental questions in 
multi-phase systems, both on the continuum scale and the grain/pore scale:
\begin{enumerate}
    \item Can we derive governing equations for the flow of two melts in a viscously compacting matrix?
    \item What is the arrangement and connectivity of two melt phases at textural equilibrium?
    \item Given detailed pore-scale simulations, what are the appropriate constitutive laws at the continuum scale?
\end{enumerate}

\subsubsection*{Feldstein et al. (2001) \cite{Feldstein2001}:}

\begin{enumerate}
    \item Disequilibrium partial melting of chondritic material: L6 chondrite Leedey
    \item Conditions: fO2 IW-1, T = 1200
    \item both silicate and metal-sulfide melts compositionally heterogeneous
    \item a few percent silicate melting
\end{enumerate}
\section{Dynamical models}

\subsubsection*{Sramek et al. (2012) \cite{Sramek2012}:}


\bibliographystyle{unsrt}
\bibliography{mendeley}

\end{document}
